### 2020-12-21 paper/localpsf.tex
improved point picking algorithm box

	\While{$P$ is not empty}{
		Determine the point $p \in P$ that is farthest from all points in previous sample point batches

@@

		\If{$\text{point\_is\_acceptable}(p, S_b)$}{

@@

			Remove all points $q$ with $\mu(q) \in E_p$ from $P$
		}
	}

    \SetKwFunction{FMain}{point\_is\_acceptable}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\FMain{$p$, $S_b$}}{

	$p\text{\_is\_acceptable} \gets \text{True}$

	$E_p$ is the ellipsoid associated with $p$ (see \eqref{eq:support_ellipsoid})

	\For{$q \in S_b$}{

		$E_q$ is the ellipsoid associated with $q$

		\If{$E_p \cap E_q \neq \{\}$}{

			$p\text{\_is\_acceptable} \gets \text{False}$

			Terminate for loop
		}
	}
	\textbf{return} $p\text{\_is\_acceptable}$ 
}

>>>>

	\While{$P$ is not empty}{
		Determine the point $p \in P$ that is farthest from all points in the previous sample point batches $S_1,\dots,S_{b-1}$

@@

%		\If{$\text{point\_is\_acceptable}(p, S_b)$}{
		\If{$E_p \cap E_q \neq \{\}$ for all $q \in S_b$}{

@@

			Remove all points $x$ satisfying $\mu(x) \in E_p$ from $P$
		}
	}

    \SetKwFunction{FMain}{point\_is\_acceptable}
%\SetKwProg{Fn}{Function}{:}{}
%\Fn{\FMain{$p$, $S_b$}}{
%	
%	$p\text{\_is\_acceptable} \gets \text{True}$
%	
%	$E_p$ is the ellipsoid associated with $p$ (see \eqref{eq:support_ellipsoid})
%	
%	\For{$q \in S_b$}{
%		
%		$E_q$ is the ellipsoid associated with $q$
%		
%		\If{$E_p \cap E_q \neq \{\}$}{
%			
%			$p\text{\_is\_acceptable} \gets \text{False}$
%			
%			Terminate for loop
%		}
%	}
%	\textbf{return} $p\text{\_is\_acceptable}$ 
%}
